\documentclass[a4paper,11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[top=1.2cm,bottom=1.2cm,left=1.5cm,right=1.5cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\pagestyle{empty}
\setlist[itemize]{nosep,topsep=0pt,partopsep=0pt,itemsep=2pt,parsep=0pt,leftmargin=*}
\raggedright
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}

\newcommand{\header}[1]{%
    \vspace{4pt}%
    {\large\bfseries\scshape #1}%
    \hrule height 0.4pt%
    \vspace{2pt}%
}

\begin{document}

\begin{center}
    {\Huge\scshape Jane Engineer} \\[2pt]
    Sydney, Australia $\cdot$
    \href{mailto:jane@example.com}{jane@example.com} $\cdot$
    \href{https://example.com}{example.com}
\end{center}

\vspace{-6pt}

\header{Experience}

\textbf{\href{https://example.com}{Example Corp}} \hfill Sydney, NSW \\
\textit{Staff Engineer} \hfill 2023 -- Present
\begin{itemize}
    \item Led the migration of the company's build system from Make
        to Bazel, reducing average local builds from 8\,min to 90\,s
        and shrinking CI compute spend by 40\%.
    \item Designed and implemented internal Bazel rule sets for
        TypeScript, Python, and LaTeX. The LaTeX one is now open
        source: \href{https://github.com/nicklambourne/rules_latex}{nicklambourne/rules\_latex}.
    \item Mentored four engineers through Bazel onboarding;
        co-authored an internal contribution guide.
\end{itemize}

\textit{Senior Software Engineer} \hfill 2020 -- 2023
\begin{itemize}
    \item Owned the API gateway service: 10k req/s peak, 99.97\% SLO.
    \item Drove a quarterly engineering-excellence program that
        improved Tier-1 service reliability by two nines.
\end{itemize}

\header{Education}

\textbf{University of Queensland} \hfill Brisbane, QLD \\
B.\,Sc.~Computer Science, First Class Honours \hfill 2016 -- 2019

\header{Selected Open-Source Contributions}

\begin{itemize}
    \item \href{https://github.com/nicklambourne/rules_latex}{\textbf{rules\_latex}}
        --- Bazel rules for building LaTeX documents with Tectonic.
        Bzlmod-only, toolchain-based, in-browser live preview with
        SyncTeX.
    \item Various smaller patches to Bazel, Tectonic, and a handful
        of CTAN packages.
\end{itemize}

\header{Skills}

\textbf{Build systems}: Bazel (rule authoring, toolchains, remote
execution), Make, ninja. \\
\textbf{Languages}: TypeScript, Python, Go, Rust, Starlark, C++. \\
\textbf{Distributed systems}: Kubernetes, gRPC, distributed tracing,
event-driven architectures.

\end{document}
